How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

The late emergence of substantial configurational anisotropy may seem
like a spurious effect that is particular to the one simulation shown in
Figure~\ref{fig3}. However, statistical analysis of many simulations will show this feature to emerge robustly in simulations featuring a relatively large number of bodies $M \ge 60$.

@@

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering
\includegraphics[width = 0.9 \textwidth]{./figs/fig5.pdf}
\caption{Permeability and anisotropy statistics from an ensemble of simulations. (a)--(b) Measurements of the longitudinal (a) and transverse (b) permeability are well separated with respect to the number of bodies, $M$. For each $M$, the mean and standard deviation of permeability are shown for increasing porosity (or time). (c) In all runs, the anisotropy grows substantially and reaches a maximum value of roughly 4--6. Runs with a large number of bodies ($M$ = 60, 80, or 100) show a second surge in anisotropy near the end of the simulation. (d)--(e) The configurational and shape contributions of anisotropy. While the shape anisotropy varies fairly regularly with time across all runs, the configurational anisotropy shows a distinct peak late in the simulation for runs with large $M$.
\label{fig5}
}
\end{figure*}
%---------------------------------------------------------%

>>>>

The late emergence of substantial configurational anisotropy may seem
like a spurious effect that is particular to the simulation shown in
Figure~\ref{fig3}. However, statistical analysis of many simulations will show this feature to emerge robustly in simulations featuring a relatively large number of bodies $M \ge 60$.

@@

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering
\includegraphics[width = 0.9 \textwidth]{./figs/fig5.pdf}
\caption{Permeability and anisotropy statistics from an ensemble of simulations. (a)--(b) Measurements of the longitudinal (a) and transverse (b) permeability are well separated with respect to the number of bodies, $M$. For each $M$, the mean and standard deviation of permeability are shown against increasing porosity (or time). (c) In all runs, the anisotropy grows substantially and reaches a maximum value of roughly 4--6. Runs with a large number of bodies ($M$ = 60, 80, or 100) show a second surge in anisotropy near the end of the simulation. (d)--(e) The configurational and shape contributions of anisotropy. While the shape anisotropy varies fairly regularly with time across all runs, the configurational anisotropy shows a distinct peak late in the simulation for runs with large $M$.
\label{fig5}
}
\end{figure*}
%---------------------------------------------------------%
